% resume.tex
% vim:set ft=tex spell:

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Matt Scudder}}

1851 Bonneville Drive\ \ \textbullet
\ \ Orlando, FL 32826
\\
(218) 666-8626\ \ \textbullet
\ \ mattscudder@gmail.com
\end{center}

\hrule
\subsection*{Objective}
My goals are to increase familiarity with physics engines and to gain further knowledge on game programming. My interests include game programming and autonomous robotics. \\

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{University of Central Florida}}
		{\textbf{Orlando, FL}}
	\\
	\headerrow
		{\emph{Interdisciplinary Studies Major}}
		{\emph{Graduation Dec. 2015}}
	\begin{itemize*}
		\item Interdisciplinary Studies with the main focus being in Computer Science and secondary focuses being in Physics and Psychology.
		\item The combination of Computer Science, Physics and Psychology is beneficial to game design due to the recent interest in accurate physics in games as well as a psychology background that helps to create intuitive user interfaces.  
	\end{itemize*}

		\item
	\headerrow
		{\textbf{Pine View School for the Gifted}}
		{\textbf{Osprey, FL}}
	\\
	\headerrow
		{\emph{}}
		{\emph{Graduation 2007}}
	\begin{itemize*}
		\item Ranked 6th best high school in the nation in 2007 by U.S. News.
	\end{itemize*}



\end{itemize}






\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	C, Java, \LaTeX, Python
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Side Projects}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Android App Creation}}
		{\emph{Spring 2015}}
	\begin{itemize*}
		\item Created a card selector for the Dominion card game.
		\item Created a remote to show a file selector and video player remote for the command line omxplayer on a raspberry pi using ssh as a backend.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Custom Quadcopter}}
		{\emph{Winter 2014 - Current}}
	\begin{itemize*}\item Built a quadcopter from scratch using an Arduino Uno as the fight controller. Modifications for the flight controller software are still under progress. 
	\end{itemize*}

	\item
	\headerrow
		{\textbf{redshift}}
		{\emph{Spring 2014}}
	\begin{itemize*}\item A Python Asteroids clone with an incentive for movement written for the Pygame framework.
	\end{itemize*}
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Extracurricular}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Eagle Scout}}

	\begin{itemize*}
		\item Only 4\% of registered scouts attain the rank of Eagle.
	\end{itemize*}
	\item
	\headerrow
		{\textbf{National Youth Leadership Training Staff}}

	\item
	\headerrow
		{\textbf{Member of UCF Ultimate Team: Havoc}}


\end{itemize}

\end{document}
